Human Capital Model

### 2016-02-01 Tex/paper.tex
12

Our strategy focus on two variables, $v_h$ and $u_h$. Several pairs of data are tested to find the best strategy.
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
      &$v_h$  &$u_h$        \\ \hline
 1    &             & 5              \\ \hline
 2    &             & 1              \\ \hline
 3    &             & 3              \\ \hline
 4    &             & 4              \\ \hline
\end{tabular}
\end{center}

@@

\subsection{Effects of Motion}
\label{sec:effects of motion}
When the person in the bathtub make motions, the heat exchange coefficient between person and water ${\gamma}_2$ increases. That means heat exchange between water and person increases.

In another aspect, the air above flow, so that evaporation heat of water increases.

\subsection{Effects of Bubble Bath Additive}
\label{sec:effects of bubble bath additive}

>>>>

Our strategy focus on two variables, $v_h$ and $u_h$. Nine pairs of data are tested to find the best strategy.
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
      &$v_h$  &$u_h$        \\ \hline
 1    &0.1             & 50              \\ \hline
 2    &0.2             & 50              \\ \hline
 3    &0.3             & 50              \\ \hline
 4    &0.1             & 40              \\ \hline
 5    &0.2             & 40              \\ \hline
 6    &0.3             & 40              \\ \hline
 7    &0.1             & 30              \\ \hline
 8    &0.2             & 30              \\ \hline
 9    &0.3             & 30              \\ \hline
\end{tabular}
\end{center}

@@

\subsection{Effects of Motion}
\label{sec:effects of motion}
When the person in the bathtub make motions, the heat exchange coefficient between person and water ${\gamma}_2$ increases. That means heat exchange between water and person increases. In another aspect, the air above flow, so that evaporation heat of water increases. Water losses more heat.

The effect is that more heat is called for to keep the temperature. So $u_h$ increases for best strategy to keep the temperature.

\subsection{Effects of Bubble Bath Additive}
\label{sec:effects of bubble bath additive}
When bubble bath additive is added while initially filling the bathtub, bubble stay on the surface and restraint the evaporation of water to air. So water losses less heat.

The effect is that less heat is called for to keep the temperature. So $u_h$ decreases for best strategy to keep the temperature.
